Block bootstrap consistency\\under weak assumptions

### 2015-12-31 Paper.tex

First, the relevant probability infrastructure.  Let
$(S, \Omega, \pr)$ be a probability space and define the sequence of
sub-sigma-fields $\Omega_n \subset \Omega$. Assume that each
$X_{nt}$, $V_{nt}$, $M_{nj}$, and $u_{nj}$ is $\Omega_n$-measurable,
with $u_{nj}$ the $\operatorname{uniform}(1,\dots,n)$ random variables
that designate the start period of each bootstrap ``block.'' Also
define the \sigmafield\ generated by the stationary bootstrap's block
lengths alone,
\begin{equation}
  \Ms = \sigma(J_{n}, M_{n1},\dots,M_{nJ_n})
\end{equation}
and the conditional probability $\Pm(\cdot) = \pr[\cdot \mid \Ms]$.
(And define $\Pm^*(\cdot) = \pr^*[\cdot \mid \Ms]$, $\Em(\cdot) =
\E^*(\cdot \mid \Ms)$, etc.) An important property is
that $\Ms$ is \emph{independent} of the $X_{nt}$'s, $V_{nt}$'s, and
$u_{nj}$'s, so we can treat any
$M_{nj}$ and $J_n$ terms as constants within $\Em(\cdot)$ and
$\Pm[\cdot]$ and integrate over the unconditional distributions of the
other random variables. This property is especially important because it allows us
to use maximal inequalities and other moment inequalities for
mixingale arrays with only small modifications to construct almost sure bounds on the
conditional moments $\Em$.

>>>>

First, the relevant probability infrastructure.  Let
$(S, \Omega, \pr)$ be a probability space and define the sequence of
sub-sigma-fields $\Omega_n \subset \Omega$. Assume that each
$X_{nt}$, $V_{nt}$, $M_{nj}$, and $u_{nj}$ is $\Omega_n$-measurable,
with $u_{nj}$ the $\operatorname{uniform}(1,\dots,n)$ random variables
that designate the start period of each bootstrap ``block.'' Also
define the \sigmafield\ generated by the stationary bootstrap's block
lengths alone,
\begin{equation}
  \Ms = \sigma(J_{n}, M_{n1},\dots,M_{nJ_n})
\end{equation}
and the conditional probability $\Pm(\cdot) = \pr[\cdot \mid \Ms]$.
(And define $\Pm^*(\cdot) = \pr^*[\cdot \mid \Ms]$, $\Em(\cdot) =
\E^*(\cdot \mid \Ms)$, etc.) An important property is
that $\Ms$ is \emph{independent} of the $X_{nt}$, so we can treat any
$M_{nj}$ and $J_n$ terms as constants within $\Em(\cdot)$ and
$\Pm[\cdot]$ and integrate over the unconditional distributions of the
$X_{nt}$. This property is especially important because it allows us
to use maximal inequalities and other moment inequalities for
mixingale arrays without modification to construct almost sure bounds on the
conditional moments $\Em$.

### 2015-12-31 subs/ETr2/reply_2.tex

>>>>

  The important point to keep in mind is that $\mathcal{M}$ only
  contains information about the block lengths for the stationary
  bootstrap. Lemmas 5 and 6 present results for the unconditional
  expectation that hold for \emph{every fixed} block length ($m'$ in
  Lemma 5, $m$ in Lemma 6). Uniform integrability over the family of
  block lengths (as in Lemma 5) implies that the same $B(\cdot)$
  applies to every $m'$ in $1,\dots,n$. Then on page 9, we use the
  fact that the same $B(\cdot)$ works for every $m'$ implies that it
  works for a randomly chosen $m'$ as well.

  I've added an intermediate step in that application of Lemma 5 to
  try to make the argument less opaque.

  The use of Lemma 6 is similar. In that expression, $M_{nj}$ is
  measurable with respect to $\mathcal{M}_n$, so it is treated the
  same as the constant $m$ in the statement of Lemma 6, and the other
  random variables are independent of $\mathcal{M}_n$. I have added
  some additional explanation that (I hope!) make this point more clear.
